---
title: "gtsummary in quarto"
format: 
  html:
    theme: quartz
execute:
  eval: true
  echo: false
---

```{r}
#| message: FALSE
#| echo: FALSE
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

```{r}
#| label: tbl-one
#| tbl-cap: "This is a great table"

tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
mean_sleep <- mean(nlsy$sleep_wknd, na.rm = TRUE)
median_sleep <- median(nlsy$sleep_wknd, na.rm = TRUE)
```
I want to add `r 3+4` participants.

The average amount of sleep on the weekends was `r mean_sleep` hours.
The median amount of sleep on the weekends was `r median_sleep` hours.

The average amount of sleep on the weekends was  `r mean(nlsy$sleep_wknd, na.rm = TRUE)` 
The median amount of sleep on the weekends was  `r median(nlsy$sleep_wknd, na.rm = TRUE)` 

```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
table1 <- tbl_summary(
  nlsy,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wknd))
table1
```

```{r}
inline_text(table1, variable = "sleep_wknd")
```

The overall median number of hours of sleep was (`r inline_text(table1, variable = "sleep_wknd")`).

```{r}
#| label: tbl-sleep
#| tbl-cap: "descriptive statistics stratified by sex with sleep"
table_sex_sleep<-tbl_summary(
	nlsy,
	by = sex_cat,
	include = c(sleep_wknd, race_eth_cat, region_cat, eyesight_cat, glasses, age_bir)) |>
		add_overall()

table_sex_sleep
inline_text(table_sex_sleep, variable = "sleep_wknd", column = "stat_1")
inline_text(table_sex_sleep, variable = "eyesight_cat", level = "Excellent", column = "stat_0")
```

